Convective penetration is set by the flux and dissipation, not the stiffness

### 2021-05-29 manuscript/ms.tex
close to a draft for co-authors

%%%% Custom commands
\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
\newcommand{\delp}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\Fcz}{\ensuremath{F_{\rm{cz}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\mD}{\ensuremath{\mathcal{D}}}
\newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Lcz}{\ensuremath{L_{\rm{cz}}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand\Pran{\ensuremath{\mathrm{Pr}}}
\newcommand{\brunt}{Brunt-V\"{a}is\"{a}l\"{a}}

@@

\shorttitle{SHORT TITLE}
\shortauthors{Anders et al}

@@

%%%% Title and Abstract
\title{This is a title}
\author[0000-0002-3433-4733]{Evan H. Anders}
\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
\author[0000-0001-5048-9973]{Adam S. Jermyn}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}
\author[0000-0002-7635-9728]{Daniel Lecoanet}
\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
\affiliation{Department of Engineering Sciences and Applied Mathematics, Northwestern University, Evanston IL 60208, USA}
\author[0000-0001-8935-219X]{Benjamin P. Brown}
\affiliation{Department Astrophysical and Planetary Sciences \& LASP, University of Colorado, Boulder, CO 80309, USA}

@@

\begin{abstract}
Blah Blah short description
\end{abstract}
\keywords{UAT keywords}

%%%% Body of paper
\section{Introduction}
\label{sec:introduction}
Convection is a crucial heat transport mechanism in essentially all stars \citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}.
Convective dynamics drive many still poorly-understood phenomena in stars.
For example, convection drives the magnetic dynamo of the Sun, leading to the host of emergent phenomena known as solar activity \citep{brun_browning_2017}.
Convection is also responsible for compositional mixing, which can modify surface abundances or inject additional fuel into convective cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
Furthermore, convective motions excite both acoustic and gravity waves, which can be observed and used to constrain the thermodynamic structure of stars \citep{aerts2010, basu2016}.
A complete and nuanced understanding of convection is therefore crucial for understanding stellar structure, evolution, and observations.

One aspect of stellar convection which remains poorly understood despite decades of study is the class of mechanisms generally referred to as ``convective overshoot.''
Broadly, in the stellar structure literature, convective overshoot refers to any mechanism which causes at least compositional mixing beyond the Schwarzschild or Ledoux stable convective boundary.
Improved models of overshoot could resolve many discrepancies between observations and structure models.
For example, observed surface lithium abundances in the Sun and solar-type stars align poorly with models, which could suggest a need for additional mixing below the solar convection zone \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021}; model and observation discrepancies can be reduced by appropriately incorporating mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
There is also ample evidence from massive stars with core convection that currently-employed prescriptions of convective overshoot are inadequate \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convective overshoot and mixing beyond convective boundaries \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}.
While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
In short, in order to resolve many of the discrepancies between current stellar evolution models and observations, we must come to a more complete, and \emph{parameterizeable} understanding of the manner in which convective motions extend beyond convective boundaries.

The host of mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
The first of these classes is, confusingly, also called ``convective overshoot'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly \emph{do not adjust the thermodynamic profile}.
The second of these classes is called ``convective penetration,'' in which convective motions mix the thermodynamic profiles beyond the convective boundary, thereby extending the convective boundary beyond the nominal Schwarzschild or Ledoux one.
We will follow a deep history \citep{zahn1991, korre_etal_2019} and use this terminology throughout this work.
The primary focus of this work will be on convective penetration, as this mechanism shows promise in aligning observations and models \citep{christensen-dalsgaard_etal_2011, pedersen_etal_2021}.

Convective overshoot and penetration have been studied in laboratory experiments and numerical simulations for decades, and has been reviewed by many authors \citep{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
Experiments and simulations exhibiting extensive convective penetration in simplified, Boussinesq setups have been studied for decades \citep{ musman1968, deardorff_etal_1969, moore_weiss_1973}, with multiple recent studies suggesting that the penetration depth (or overshoot depth) is highly dependent on the stiffness of the radiative-convective interface \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018, korre_etal_2019}.
Some studies in density-stratified or fully compressible, stratified systems \citep[e.g.,][]{hurlburt_etal_1986, saikia_etal_2000} also found significant penetration depths, with multiple authors finding results suggesting that penetration and overshoot depths were determined by the stiffness of the radiative-convective interface \citep{hurlburt_etal_1994, singh_etal_1995, browning_etal_2004, dietrich_wicht_2018}.
However, a number of studies have contradicted these results, showing little to no dependence on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
Many modern simulations utilize stellar structure models as inspiration for their experimental setup, and find significant convective overshoot or penetration \citep{browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
Some simulations have found that the extension beyond the convection zone depends strongly on the input flux for their experimental setups \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
In this work, we follow the results of these last class of simulations and study how one aspect of the convective flux modifies the extent of the penetration region.

\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that the boosting of luminosity in stellar experiments compared to reference stars may be leading to wrong estimates of the penetrative dynamics.
Indeed, some simulations have shown partial agreement with these ideas.
In the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994, rogers_etal_2006} agree with Zahn's theory (although at high stiffness they disagree).
Some simulations have used the magnitude of the system flux as a control parameter, and indeed found that the penetration depth was dependent on it \citep{singh_etal_1998, hotta2017, kapyla2019}.
These results suggest that Zahn's theory deserves to be revisted.

In this work, we design two numerical experiments to test the theory of \citet{zahn1991}.
We use a modified incompressible, Boussinesq model to study the simplest possible system, and re-derive his theory in our simplified limit.
The results of our simulations are in full agreement with Zahn's theory.
\begin{quote}
\emph{
Specifically, we find that the depth of convective penetration depends on the gradient of the radiative flux near the convective boundary.
}
\end{quote}
Thus, the penetration depth can be approximated so long as the radiative conductivity, or likewise the opacity, is known at the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, re-derive the theory of \citet{zahn1991}, and retrieve predictions for our two experimental designs from that theory.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can put finer constraints on this theory in Sec.~\ref{sec:discussion}.

@@

\subsection{Equations}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a (constant) background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[as in e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
These equations are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
The classic Boussinesq thermal diffusion term $\chi \grad^2 T'$ therefore carries no flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and primes ($'$) represent fluctuations away from those horizontal means.
Throughout this work, we will consider Cartesian coordinates $(x, y, z)$, but this analysis is generalizeable to spherical geometry.
We will furthermore assume a model in which an unstable convection zone sits below a stable radiative zone, but this analysis also holds for the inverted problem.

%\subsection{Vertical momentum equation balances}
%\label{sec:theory_momentum}
%Assuming a vertical and uniform gravitational acceleration $\vec{g} = -g\hat{z}$, the vertical component of Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq} is
%\begin{equation}
%\partial_t w + (\vec{u}\dot\grad)w = -\frac{1}{\rho_0}\partial_z p + |\alpha|g T + \nu\grad^2 w.
%\label{eqn:momentum_z}
%\end{equation}
%We next horizontally average this equation; under the assumption that $\overline{w} = 0$ at some height (e.g., at an impenetrable boundary), Eqn.~\ref{eqn:incompressible} requires $\overline{w}$ = 0 everywhere.
%The horizontally-averaged equation is therefore
%\begin{equation}
%\frac{1}{\rho_0}\frac{d \overline{p}}{dz} = |\alpha| g \overline{T} - \overline{(\vec{u}\dot\grad)w} + \nu\overline{\grad_h^2 w},
%\end{equation}
%where $\grad_h^2 = \partial_x^2 + \partial_y^2$.
%At this point we decompose $\overline{p} = \overline{p_s} + \overline{p_d}$, where $p_s$ is the ``structure'' component of of the pressure whose gradient balances the buoyant gradient (providing hydrostatic balance), and $p_d$ is the dynamical pressure whose mean balances the mean contributions of advection and dissipation.
%Accordingly, we define $\tilde{p} \equiv p - \overline{p_s}$, removing the mean structure component of the pressure.
%This construction leaves fluctuations ($p'$ and $\overline{p_d}$) which are set by the convective dynamics.
%Taking a time-average of Eqn.~\ref{eqn:momentum_z} and assuming that convection reaches a statistically stationary state and that viscous dissipation is unimportant \citep[which is a common assumption, but may not always apply in stellar contexts per][]{currie_browning_2017}, we retrieve
%\begin{equation}
%\frac{1}{\rho_0}\frac{\partial \tilde{p}}{\partial z} = |\alpha| g T' - (\vec{u}\dot\grad)w.
%\label{eqn:fluc_momentum_z}
%\end{equation}
%In other words, convection reaches a state in which fluctuating buoyancy forces and nonlinear advection come into a balance and saturate at similar magnitudes.
%The pressure gradient rises to a similar magnitude to regulate the flows and ensure Eqn.~\ref{eqn:incompressible} is satisfied (and a similar argument could be made for e.g., anelastic convection).
%As a result, we can estimate that each of the terms in this equation have similar magnitudes,
%\begin{equation}
%\frac{1}{\rho_0}\frac{\partial \tilde{p}}{\partial z} \sim |\alpha| g T' \sim (\vec{u}\dot\grad)w.
%\label{eqn:momentum_balance}
%\end{equation}

\subsection{Kinetic energy \& the vorticity-flux link}
\label{sec:theory_energy}
Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
= \alpha g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
Assuming a statistically stationary state, and assuming that the kinetic energy fluxes vanishes at the upper and lower boundaries of the convection zone, this equation permits one solution,
\begin{equation}
\alpha g \angles{\Fconv} = \nu\angles{|\vec{\omega}|^2},
\label{eqn:ke_averages}
\end{equation}
where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
It is counterintuitive to find that a viscous term is on the same order of magnitude as the convective flux.
However, this term dimensionally behaves like $\nu u^2 / \ell^2$, where $\ell$ is the length scale of velocity gradients; if the average vorticity is dominated by gradients at the dissipation scale, then it makes sense that this term can persist even at small values of $\nu$.
Furthermore, \citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of the viscous heating term remains large for turbulent flows.
Since $\nu |\vec{\omega}^2|$ is the Boussinesq analog to the viscous heating, the importance of this term is perhaps not too surprising.

>>>>

%%%% Custom commands
\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
\newcommand{\justgrad}{\ensuremath{\nabla}}
\newcommand{\delp}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\Fcz}{\ensuremath{F_{\rm{cz}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\mD}{\ensuremath{\mathcal{D}}}
\newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Lcz}{\ensuremath{L_{\rm{cz}}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand\Pran{\ensuremath{\mathrm{Pr}}}
\newcommand{\brunt}{Brunt-V\"{a}is\"{a}l\"{a}}

@@

\shorttitle{Convective Penetration}
\shortauthors{Anders et al}

@@

%%%% Title and Abstract
\title{Convective penetration is set by the flux and dissipation, not the stiffness}
\author[0000-0002-3433-4733]{Evan H. Anders}
\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
\author[0000-0001-5048-9973]{Adam S. Jermyn}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}
\author[0000-0002-7635-9728]{Daniel Lecoanet}
\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
\affiliation{Department of Engineering Sciences and Applied Mathematics, Northwestern University, Evanston IL 60208, USA}
\author[0000-0001-8935-219X]{Benjamin P. Brown}
\affiliation{Department Astrophysical and Planetary Sciences \& LASP, University of Colorado, Boulder, CO 80309, USA}

@@

\begin{abstract}
Convection is a crucial heat transport mechanism and excitation mechanism in planets and stars.
While parameterizations like mixing length theory adequately describe convection in bulk convection zones, the behavior of convective motions near and beyond the Schwarzschild-stable convective boundary are not well understood.
In this paper, we examine a simplified Boussinesq model of stellar convection with a radiative flux.
We derive a ``penetration parameter'' $\mathcal{P}$ which compares how quickly the radiative gradient deviates from the adiabatic on either side of the convective boundary.
In line with \citet{zahn1991}, we predict that the extend of the adiabatically stratified penetrative layer is strongly related to the magnitude of $\mathcal{P}$.
We perform 3D numerical simulations using Dedlaus to test this theory, and find that the penetrative region strongly depends on the flux-based $\mathcal{P}$ and only weakly depends on the degree of turbulence in the flows or on the stiffness of the convective interface.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and our results suggest that convection zones may extend beyond the Schwarzschild boundary by some 20\% of a mixing length.
We briefly examine a MESA solar model in which the bottom boundary of the convection zone is set according to our theory, and discuss the possible implications and future paths necessary for these findings.
\end{abstract}
\keywords{UAT keywords}

%%%% Body of paper
\section{Introduction}
\label{sec:introduction}
Convection is a crucial heat transport mechanism in stars \citep{woosley_etal_2002, hansen_etal_2004, christensen-dalsgaard_2021}, and convective dynamics influence many poorly-understood stellar phenomena.
For example, convection drives the magnetic dynamo of the Sun, leading to the host of emergent phenomena known as solar activity \citep{brun_browning_2017}.
Convection also mixes stars compositionally, which can modify observed surface abundances or inject additional fuel into convective cores, thereby extending stellar lifetimes \citep{salaris_cassisi_2017}.
Furthermore, convective motions excite waves, which can be observed and used to constrain the thermodynamic structure of stars \citep{aerts2010, basu2016}.
A complete and nuanced understanding of convection is therefore crucial for understanding stellar structure, evolution, and observations.

Despite decades of study, robust parameterizations for the mechanisms broadly referred to as ``convective overshoot'' remain elusive, and improved parameterizations could resolve many discrepancies between observations and structure models.
In the stellar structure literature, ``convective overshoot'' refers to any convectively-driven mixing which occurs beyond the boundaries of the unstable convection zone.
This mixing can influence, for example, observed surface lithium abundances in the Sun and solar-type stars which align poorly with models \citep{pinsonneault1997, carlos_etal_2019, dumont_etal_2021}.
Furthermore, modern spectroscopic observations suggest a lower solar metallicity than previously thought, and models computed with modern metallicity estimates and opacity tables have shallower convection zones than helioseismic observations suggest \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021}; modeling and observational discrepancies can be reduced with additional mixing below the convective boundary \citep{christensen-dalsgaard_etal_2011}.
There is also ample evidence from massive stars with core convection that currently-employed prescriptions of convective overshoot are inadequate \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021, pedersen_etal_2021}.
Since core convective overshoot increases the reservoir of fuel available for nuclear fusion at each stage in stellar evolution, improved models of core convective boundary mixing could have profound impacts on the post-main sequence evolution and remnant formation of massive stars \citep{farmer_etal_2019, higgins_vink_2020}.
In order to ensure that models can be evolved on fast (human) timescales, 1D stellar evolution codes rely on simple parameterizations of convective overshoot and mixing beyond convective boundaries \citep{shaviv_salpeter_1973, maeder1975, herwig2000, paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}, such as the classic Mixing Length Theory \citep{bohm-vitense1958}.
While some preliminary work has been done to couple 3D dynamical convective simulations with 1D stellar evolution codes \citep{jorgensen_weiss_2019}, these calculations are currently prohibitively expensive to perform e.g., at every timestep in a stellar evolution calculation.
In short, in order to resolve many of the discrepancies between current stellar evolution models and observations, we must come to a more complete, and \emph{parameterizeable} understanding of the manner in which convective motions extend beyond convective boundaries.

The mechanisms referred to as ``convective overshoot'' in the stellar literature fall into two hydrodynamical classes.
The first class is, confusingly, also called ``\emph{convective overshoot}'' in the fluid dynamics literature and refers to motions which extend beyond the convective boundary and mix chemical compositions but importantly do not adjust the thermodynamic profile.
The second class is called ``\emph{convective penetration},'' and refers to convective motions which mix the thermodynamic profiles beyond the convective boundary, thereby extending the extent of the extent of the adiabatically-mixed convective region.
We will follow a deep history \citep{zahn1991, brummell_etal_2002, korre_etal_2019} and use this terminology; the primary focus of this work is convective penetration.

Convective overshoot and penetration have been studied in the laboratory and through numerical simulations for decades, and the state of the field has been regularly reviewed \citep[e.g.,][]{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
One parameter which is commonly linked to penetration or overshoot is the ``stiffness'' of the radiative-convective interface; the stiffness is a ratio which states how stable a radiative zone is compared to an adjacent convection zone according to some measure like a dynamical frequency or characteristic entropy gradient.
Experiments and simulations exhibiting extensive convective penetration in water or other simplified, Boussinesq setups have a long history \citep{ musman1968, deardorff_etal_1969, moore_weiss_1973}.
Some of these recent simplified studies suggest that the penetration depth is highly dependent on the stiffness of the radiative-convective interface \citep{couston_etal_2017, toppaladoddi_wettlaufer_2018}, and some find very little penetration but significant stiffness-dependent overshoot \citep{korre_etal_2019}.
Some studies in density-stratified or fully compressible, stratified systems \citep[e.g.,][]{hurlburt_etal_1986, saikia_etal_2000} also found significant penetration depths, with multiple authors finding results suggesting that both penetration and overshoot depths were determined by the stiffness \citep{hurlburt_etal_1994, singh_etal_1995, browning_etal_2004, dietrich_wicht_2018}.
However, some studies have contradicted these results, showing little to no dependence on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
Many modern simulations utilize stellar structure models as background states and find significant convective overshoot and/or penetration \citep{browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
This host of experiments indeed suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.

A few flux-based theories of convective penetration have been historically considered.
\citet{roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998} derived an ``integral constraint'' from the energy conservation equation and found that the integral of the flux over the full convective and penetrative region must be balanced by the dissipation of energy on small scales, which places an upper limit on the depth of the penetrative region.
\citet{zahn1991} theorized that convective penetration should depend only on how steeply the radiative temperature gradient varies at the convective boundary.
Following \citet{zahn1991}'s work, \citet{rempel2004} derived a semianalytic model and suggested that inconsistencies seen in simulations of penetrative dynamics can be explained by the magnitude of the fluxes or luminosities driving the simulations.
Indeed, some simulations have tested this exact idea, and found that penetration depths depend strongly on the input flux \citep{singh_etal_1998, kapyla_etal_2007, tian_etal_2009, hotta2017, kapyla2019}.
Furthermore, in the limit of low stiffness, the simulations of \citet{hurlburt_etal_1994} and \citet{rogers_etal_2006} seem to agree with Zahn's theory (although at high stiffness they disagree).
In light of these results, Roxburgh's integral constraint and Zahn's theory deserve to be revisited.

In this work, we design two numerical experiments to test \citet{zahn1991}'s idea that the penetration depth depends on the shape of the radiative gradient at the convective boundary.
We use a modified incompressible, Boussinesq model to study the simplest possible system, and use \citet{roxburgh1989}'s constraint to derive a theory analogous to \citet{zahn1991}'s in this simplified limit.
\begin{quote}
\emph{
We find that the extent of convective penetration depends strongly on the shape and magnitude of the radiative gradient near the convective boundary.
}
\end{quote}
Thus, the penetration depth can be calculated using the radiative conductivity (or opacity) around the convective boundary.

We present these findings as follows.
In Sec.~\ref{sec:theory}, we describe our modified Boussinesq equations, derive a theory of convective penetration similar to \citet{zahn1991}'s, and retrieve predictions for our two experimental designs from that theory.
In Sec.~\ref{sec:simulation_details}, we describe our simulation setup and parameters.
In Sec.~\ref{sec:results}, we present the results of these simulations, with a particular focus on the depth of the penetrative regions.
In Sec.~\ref{sec:solar_model}, we create and discuss a solar MESA model which uses this theory to determine the bottom of the solar convection zone.
Finally, we discuss how future simulations can put finer constraints on this theory in Sec.~\ref{sec:discussion}.

@@

\subsection{Equations}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that studied by e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
The equations we use are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
The classic thermal diffusion term $\chi \grad^2 T'$ therefore carries no flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Finally, we will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.

\subsection{Kinetic energy \& the dissipation-flux link}
\label{sec:theory_energy}
Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
= \alpha g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
Assuming a statistically stationary state, and assuming that the kinetic energy fluxes vanishes at the upper and lower boundaries of the convection zone, this equation permits one solution: \citet{roxburgh1989}'s integral constraint,
\begin{equation}
\alpha g \angles{\Fconv} = \nu\angles{|\vec{\omega}|^2},
\label{eqn:ke_averages}
\end{equation}
where $\Fconv = w T$ and angles $\angles{\,\cdot\,}$ represent a time- and volume- average.
It may seem counterintuitive to find that the viscous energy dissipation term $\nu\angles{|\vec{\omega}|^2}$ operates on the same order of magnitude as the convective flux.
However, Eqn.~\ref{eqn:ke_averages} is a statement of a balance between buoyant injection of energy into the system on large scales and dissipation on small scales.
Dimensionally, the viscous dissipation term is $\nu u^2 / \ell^2$, where $u$ is the average convective velocity and $\ell$ is the length scale of velocity gradients on the dissipation scale, and it is reasonable to assume that $\ell^2 \propto \nu$ leading to an appreciable dissipation even at very small $\nu$.
\citet{currie_browning_2017} demonstrated that even in appreciably density-stratified atmospheres, the magnitude of viscous dissipation remains large for turbulent flows, so the importance of $\nu |\vec{\omega}^2|$ is perhaps not too surprising.

We now decompose the convection zone into a zone which is classically unstable according to the Schwarzschild criterion (called the CZ, with depth $L_s$) and a dynamically distinct penetrative zone (called the PZ, with depth $\delp$).
Following Eqn.~\ref{eqn:ke_averages}, we write
\begin{equation}
\frac{1}{L_s + \delp}\left(\int_{\rm{CZ}} \bar{\Fconv} dz + \int_{\rm{PZ}} \bar{\Fconv} dz \right) = \frac{\nu}{\alpha g} \angles{|\vec{\omega}|^2}.
\label{eqn:flux_breakup}
\end{equation}
Rearranging, we retrieve 
\begin{equation}
\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} = -(1 - f),
\qquad\rm{with}\qquad
f \equiv \frac{(L_s + \delp)}{\alpha g} \frac{\nu\angles{|\vec{\omega}|^2}}{\int_{\rm{CZ}} \bar{\Fconv} dz}
= \frac{\int_{\rm{CZ+PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz},
\label{eqn:preliminary_flux_ratio}
\end{equation}
where the final equality is a tautological rearrangement of the decomposition of the flux integral in Eqn.~\ref{eqn:flux_breakup}.
The upshot of this equation is that the ratio of the flux integrals in the PZ and CZ relates to some characteristic properties of the convective dynamics (the viscous dissipation), quantified by $f$.
We theorize that $f$ is some constant which weakly depends upon things like the turbulence of the flows, the stiffness of the radiative-convective interface, etc.
If this is the case, Eqn.~\ref{eqn:preliminary_flux_ratio} represents a simple parameterization of the nature of the penetrative zone in terms of the convection zone.
In order to derive a specific penetration depth $\delp$, we must turn to a more in-depth examination of the fluxes in the PZ.

\subsection{A flux-based penetration argument}
\citet{zahn1991} and Eqn.~\ref{eqn:preliminary_flux_ratio} suggest that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
Assuming convection reaches a time-stationary state, we horizontally-average and vertically integrate Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\end{equation}
where $\Fbot$ is the flux carried at the base of the convection zone, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We next assume that convection penetrates some distance $\delp$ above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the PZ.
This assumption specifies the radiative flux in the PZ ($\bar{\Frad} = k\gradad$) which in turn specifies the convective flux.
Defining the radiative gradient $\grad_{\rm{rad}} = \Ftot/k$, we can write the PZ convective flux
\begin{equation}
\overline{\Fconv}|_{\rm{PZ}} = \Ftot - \overline{\Frad} = k(\gradrad - \gradad).
\label{eqn:fconv_pz}
\end{equation}
Within the penetrative region, $\gradad > \gradrad$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv}|_{\rm{PZ}} < 0$.
